---
title: How Quarto Works
keep-md: true

format: 
  html: 
    style: darkly 
  pdf:
    documentclass: article
    keep-tex: true

echo: false
warning: false
error: false
message: false
---

```{mermaid}
%%| fig-cap: How quarto works
flowchart LR
  markdown --> qmd
  yaml --> qmd
  code --> qmd
  qmd --> knitr
  code --> |execute|knitr
  knitr --> md
  md --> pandoc 
  pandoc --> html/pdf/epub/...
```

# Introduction

The `mtcars` dataset contains fuel consumption and automobile design details for 32 cars (1973-74 models). This brief analysis covers the dataset's structure, summary statistics, and key visualizations.

# Dataset Overview

```{r}
#| include: false
# Load necessary libraries
library(ggplot2)
ggplot2::theme_set(theme_minimal(base_size = 18))
data("mtcars")
```

# Summary Statistics

```{r}
#| echo: true

summary(mtcars[, c("mpg", "wt")])
```

# Key Visualizations

## Distribution of Miles Per Gallon (mpg)

```{r}
#| fig-cap: Histogram of mpg
#| label: fig-hist
ggplot(mtcars, aes(x = mpg)) +
  geom_histogram(binwidth = 2, fill = "steelblue", color = "black") +
  labs(title = "Distribution of Miles Per Gallon", x = "Miles Per Gallon", y = "Frequency")
```

## Relationship Between mpg and Weight

```{r}
#| fig-cap: Scatter plot of mpg vs wt
#| label: fig-scat
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(title = "mpg vs Weight", x = "Weight (1000 lbs)", y = "Miles Per Gallon")
```

# Conclusion

This brief analysis of the `mtcars` dataset provides an overview of car features and their relationships, highlighting the distribution of miles per gallon @fig-hist and its dependence on car weight in @fig-scat.
